---
title: "ADS Notes"
author: "Alexandra DeKinder, ad3540"
date: "9/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Week 1

Reproducible Data Analysis:
  - Want to establish practices that allow your work to be reproducible 
  
3 ways to do this:
  1. Set up project folder
  2. Documentation
  3. Project history and source control

Project Setup (given in starter repo):

  First identify a working folder that includes the following subfolders:
    - Data: data used in the analysis (READ ONLY)
    - Doc: the report or presentation file
    - Figs: Contains generated figures. Images for report go in doc folder
    - Lib: various files with function definitions and code
    - Output: analysis output, processed datasets, logs, or other processed things


#Week 2

Demo on two starter codes in repo project 1

In order to process data, just run Text_Processing.Rmd

NLP:
  -Speech recognition
  - NL Understanding
    - Context understanding
  - Q and A
  - NL Generation
  - Text-to-Speech
  
For sentiment analysis, use NRC Emotion Lexicon source

Topic Modeling (essentially an unsupervised algorithm)
  -Clusters documents into topics
  -Can NOT tell you how many different topics there are in a document
  



```{r}
HEllo
Goodbye

```
